A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2016-06-28 Answer_to_referee_report_LensingPaper.tex

Reviewer's Comments:
Reviewer: 1

Comments to the Author

====================================
\begin{itemize}

\item This is an interesting paper which makes neat use of the combination of stellar
kinematics and strong lensing to investigate the mass structure of the spiral galaxy
J1331. 
\Comment{Thanks. It is a very exiting galaxy that's definitely worth exploring.}

\item The introduction could be re-written slightly to emphasise the points that the study
wants to investigate; for instance, the opening paragraph talks about the methods
used rather than the astrophysics that the study is hoping to probe. This could
probably be removed altogether, and the second paragraph promoted to the beginning. 
\Comment{That is a good point. We changed the opening paragraph to a general sentence why determining the matter distribution of galaxies is important. We mention the different methods now in the third paragraph.}

\item It would also be nice to include some more discussion of the possibility of a recent
merger in the galaxy's past in the introduction, as this is a really interesting
feature of the galaxy in question and is also a very active topic of research. \Comment{Good point. 1.) We added a sentence mentioning the important role of mergers in modifying the matter distribution and added some recent references. 2.) We added a short paragraph later in the introduction that points out that J1331 is a special and very interesting galaxy for researching mergers. We also explain better that this merger is one of the reasons why we especially focus on the inner regions of J1331 in our study.}

\item The manuscript in its current form is also slightly longer than necessary at certain
points: for instance, in section 3.2.1, it is not really necessary to present all
the lensing equations (e.g. the time delay, equation 7), and similarly, section
3.3.1 contains a lot of material that is implicit in Cappellari's JAM code, and
therefore does not need to be explained equation by equation here. Section 3.3.4
also rather throws the book at the NFW profile relations – it probably isn't
necessary to include equation 22. \Comment{We made an effort to remove unnecessary equations in Section 3.2.1, tighten the explanation of the derivation of the Jeans equations in Section 3.3.1 and 3.3.3 and removed big and clumsy mathematical expressions by referring to the explicit equations in the literature instead. In 3.3.2 we refer stronger to the changes we made to Capellari's JAM code and kept the corresponding equations. In Section 3.3.4 we moved equations that are definitions and therefore needed inline to make it shorter; we kept the Maccio concentration vs. halo mass relation and explicitely mention that we will use this later as a prior in our modelling. In general we include a lot of equations and a big theory introduction because it is a paper that is potentially interesting for two communities, the lensing and the dynamics community. We wanted to make the paper understandable for both.}

### 2016-06-28 LensingPaper_draft_v4.01.tex
Some corrections in the paper, a few comments in the referee report.

%--------------------------------------------
MGEs are used to parametrize the observed surface brightness (or projected total mass) of a galaxy as a sum of $N$ 2-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}. This work makes use of the algorithm and code\footnote{The IDL code package for fitting MGEs to images by \citet{Cap02} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}. The version from June 2012 was used in this work.} by \citet{Cap02}. We assume all Gaussians to have the same center and position angle $\phi$, i.e., the orientation of the Gaussians' major axis measured from North through East in the polar coordinate system $(R',\theta')$ on the plane of the sky. Then a surface brightness model can be expressed as
\begin{eqnarray}
I(R',\theta') &=& \sum_{i=1}^{N} I_{0,i} \exp\left[ - \frac{1}{2\sigma_i^2} \left(x^{'2} + \frac{y^{'2}}{q_i^{'2}}\right)\right]\label{eq:MGEgeneral}\\
\text{with } I_{0,i} &=& \frac{L_i}{2\pi \sigma_i^2 q'_i}\label{eq:centralItotalL}\\
\text{and } x'_i &=& R' \cos(\theta' - \phi)\nonumber\\
y'_i &=& R' \sin(\theta' - \phi),\nonumber
\end{eqnarray}
where $I_{0,i}$ is the central surface brightness of each Gaussian, $L_i$ its total luminosity, $\sigma_i$ its dispersion along the major axis and $q'_i$ the axis ratio between the elliptical Gaussian's major and minor axis.
%--------------------------------------------

@@

%--------------------------------------------
$I(R',\theta')$ describes the intrinsic, to 2D projected light distribution or surface density of the galaxy. Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $i$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
\begin{equation}
\nu(R,z) = \sum_i \nu_{0,i} \exp \left[-\frac{1}{2\sigma_i}\left(R^2 + \frac{z^2}{q_i^2} \right) \right], \label{eq:deprojMGE}
\end{equation}
where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane. The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
\begin{eqnarray*}
q_i^2 &=& \frac{q_i'^2 - \cos^2 i}{\sin^2 i}\\
\nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
\end{eqnarray*}
%--------------------------------------------

@@

%--------------------------------------------
The free parameters of the lens model are: the source position $(x_s',y_s')$, the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \eqref{eq:scalefreemodel}-\eqref{eq:Fourieransatz}. We want to minimize the distance between the observed image positions, $\vect{\theta}_{oi}$, and those predicted by the lensing model, $\vect{\theta}_{pi}$. To avoid having to solve the lens equation \eqref{eq:Fourierlenseq} for $\vect{\theta}_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in Equation \eqref{eq:magnificationtensor} to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $. The best fit lens model is then the one that minimizes
\begin{eqnarray}
\chi^2_\text{lens} &=& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\nonumber\\
&\simeq& \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} x_s' - \tilde{x}'_{si} \\ y_s' - \tilde{y}'_{si} \end{matrix} \right) \right|^2,\label{eq:chi2lens}
\end{eqnarray}
where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$. $\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{x}'_{si},\tilde{y}'_{si})$ the source position according to the lens equation, both evaluated at the position of the $i$-th lensing image, $\vect{\theta}_{oi}$. Following \citet{GlennEC} we add a term
\begin{equation}
\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} \label{eq:chi2shape}
\end{equation}
(with $\lambda$ being some weight factor) which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
\begin{equation}
\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape} \label{eq:chi2total}
\end{equation}
We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.

@@

%--------------------------------------------
As data we use stellar line-of-sight rotation velocities $v_\text{rot} = \langle v_\text{los} \rangle_\text{obs}$ and velocity dispersions $\sigma$ as described in Section \ref{sec:data_kinematics}. The JAM models give a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle_\text{obs}$. The root-mean-square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to 
\begin{equation*}
 v_\text{rms}^2 = v_\text{rot}^2 + \sigma^2  \stackrel{!}{=} \langle v_\text{los}^2 \rangle_\text{obs}.
\end{equation*}
\OLD{The model in Equation \eqref{eq:explicitLOSvelCap}}\NEW{The model derived from the Jeans equations as outlined in Section \ref{sec:model_JAM_JAM}} predicts the intrinsic $\langle v_\text{los}^2 \rangle_\text{intr}\equiv\langle v_\text{los}^2\rangle$ at a given position on the sky, which needs then to be modified to $\langle v_\text{los}^2 \rangle_\text{obs}$ according to the mode of observation to be comparable to the measurements. The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
\begin{equation*}
\text{AP}(x',y') \equiv \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x' < + \frac{L_x}{2}\\
& \text{and } - \frac{L_y}{2} \leq y' \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise.} \end{array} \right.
\end{equation*}
The light arriving at the spectrograph itself was subject to seeing, i.e., a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV},
\begin{equation*}
\text{PSF}(x',y')\equiv\mathscr{N}(0,\sigma_\text{seeing}=\text{FWHM}/2\sqrt{2\ln2}).
\end{equation*}
The model predictions for $\langle v_\text{los}^2 \rangle_\text{intr}$ have therefore to be convolved with the convolution kernel
\begin{eqnarray*}
K(x',y') &\equiv& (\text{PSF} \ast \text{AP})(x',y') \\
&=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right],
\end{eqnarray*}
and weighted by the surface brightness $I(x',y')$, i.e.,
\begin{eqnarray*}
I_\text{obs} &=& I \ast K\\
\langle v_\text{los}^2 \rangle_\text{obs} &=& \frac{(I \langle v_\text{los}^2\rangle_\text{intr}) \ast K}{I_\text{obs}}.
\end{eqnarray*}
\NEW{We modified the JAM code by \citet{Cap08} to use this convolution kernel with non-square pixels. The JAM code then}\OLD{If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}. The version from June 2012 was used in this work.} by \citet{Cap08}} performs the convolution numerically. We set $L_x = 0.21''$ as the width of the model pixel, and get a prediction for the actual measurements in bins of width $0.63''$, $1.26''$ and $1.89''$ \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.
%--------------------------------------------

@@

%--------------------------------------------
As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE. In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenk-White (NFW) DM halo \citep{1996ApJ...462..563N} in the dynamical model. The classical NFW profile has the form
\begin{equation}
\rho_\text{NFW}(r) \propto r^{-1} \left( r+r_s \right)^{-2} \label{eq:NFWprofile}
\end{equation}
and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo. We will use $v_\text{200}\NEW{\equiv \sqrt{GM_{200}/r_{200}}}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, \OLD{i.e.,}\NEW{ and where $M_{200} \equiv M(<r_{200}) \stackrel{!}{=} \frac 43 \pi r_{200}^3 \cdot \rho_\text{crit}(z=0)$.}
\OLD{\begin{eqnarray*}
M_\text{200} &=& M(<r_{200})\\
\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
\end{eqnarray*}}
with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}. \OLD{How much the mass is concentrated in the center of the NFW halo is given by the concentration parameter
\begin{equation}
c_{200}\equiv r_{200} / r_s. \label{eq:NFW_c}
\end{equation}}
\NEW{The mass concentration of the NFW halo is quantified by $c_{200}\equiv r_{200} / r_s$.}
There is a close relation between the concentration and halo mass in simulations \citep{1996ApJ...462..563N}. \citet{Maccio08} found this relation for the WMAP5 cosmology to be
\begin{equation}
\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
\end{equation}
(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2). \NEW{In Section \ref{sec:results_JAM_NFW} we will use this relation as prior information to guide the modelling towards realistic NFW halo shapes.}
%--------------------------------------------

@@

The scaling of the drizzled HST/WFC3 images is  $S \equiv 0.05''/\text{pixel width}$ and the total exposure time $T = 1600$ sec. Each Gaussian in the MGE has a total F814W luminosity $L_i$ (in counts) and a central surface brightness (in counts per pixel) of
\begin{equation*}
C_{0,i}\text{[counts/pixel]} = \frac{L_i[\text{counts}]}{2\pi \sigma_i[\text{pixel}]^2 q_i}.
\end{equation*}
This is then transformed into an I-band surface brightness (in $\text{mag}\times(1'')^{-2}$) via
\begin{equation}
\mu_{I,0,i} \simeq -2.5 \log_{10}\left( \frac{C_{0,i}\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel width}]^2}\right) + Z + C + A_I, \label{eq:muI_}
\end{equation}
where $Z\simeq21.62~\text{mag}$ is the zero-point from \citet{Holtzman}, updated according to \citet{Dolphin,DolphinNew}, for the photometric system of the HST/WFPC2 camera and the F814W filter, plus a correction for the difference in gain between calibration and observation. $C= 0.1~\text{mag}$ corrects for the finite aperture of the WFPC2; and $A_I =0.015~\text{mag}$ is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration. The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}. The colour-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore. The last step is to transform the surface brightness $\mu_{I,0,i}$ (in mag) to the I-band surface density $I_{0,i}$ (in $L_\odot$/pc$^2$) of the Gaussian, i.e.,
\begin{eqnarray*}
I_{0,i}[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z_d \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0,i} \right)},
\end{eqnarray*}
where the term with $z_d$ accounts for redshift dimming and $M_{\odot,I}=4.08~\text{mag}$ is the Sun's absolute I-band magnitude \citep{1998gaas.book.....B}. The luminosity $L_i$[counts] and the corresponding surface brightness density $I_{0,i} [L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}.
%--------------------------------------------

@@

%--------------------------------------------
To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the IRAF \emph{ellipse} model for J1331, which is $q'=0.42$. This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}. If a typical thickness of an oblate disk is around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination follows from 
\begin{equation*}
\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}
\end{equation*}
and a correction of $+3^\circ$ \citep{1988ngc..book.....T}. Our estimate for the inclination is therefore $i \approx 70^\circ$. Given this inclination, the 2-dimensional MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo_deprojection}).

@@

For the velocity anisotropy parameter $\beta_z$ we will again employ a uniform prior 
\begin{equation*}
p(\beta_z) = \mathscr{U}(-0.5,+0.5)
\end{equation*}
to exclude very unrealistic anisotropies. The full prior used is then
\begin{eqnarray*}
&&p(\Upsilon_\text{I,*},r_s,v_{200},\beta_z) \\
&&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta_z), 
\end{eqnarray*}
where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to the fit parameters $(v_{200},r_s)$.

>>>>

%--------------------------------------------
MGEs are used to parametrize the observed surface brightness (or projected total mass) of a galaxy as a sum of $N$ 2-dimensional, elliptical Gaussians \citep{1991ApJ...366..599B,1992A&A...253..366M,1994A&A...285..723E,1999MNRAS.303..495E}. This work makes use of the algorithm and code\footnote{The IDL code package for fitting MGEs to images by \citet{Cap02} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}. The version from June 2012 was used in this work.} by \citet{Cap02}. We assume all Gaussians to have the same center and position angle $\phi$, i.e., the orientation of the Gaussians' major axis measured from North through East in the polar coordinate system $(R',\theta')$ on the plane of the sky. Then a surface brightness model can be expressed as
\begin{align}
I(R',\theta') &= \sum_{i=1}^{N} I_{0,i} \exp\left[ - \frac{1}{2\sigma_i^2} \left(x^{'2} + \frac{y^{'2}}{q_i^{'2}}\right)\right]\label{eq:MGEgeneral}\\
\text{with } I_{0,i} &= \frac{L_i}{2\pi \sigma_i^2 q'_i}\label{eq:centralItotalL}\\
\begin{split}
\text{and } x'_i &= R' \cos(\theta' - \phi)\\
y'_i &= R' \sin(\theta' - \phi),
\end{split}
\end{align}
where $I_{0,i}$ is the central surface brightness of each Gaussian, $L_i$ its total luminosity, $\sigma_i$ its dispersion along the major axis and $q'_i$ the axis ratio between the elliptical Gaussian's major and minor axis.
%--------------------------------------------

@@

%--------------------------------------------
$I(R',\theta')$ describes the intrinsic, to 2D projected light distribution or surface density of the galaxy. Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $i$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
\begin{equation}
\nu(R,z) = \sum_i \nu_{0,i} \exp \left[-\frac{1}{2\sigma_i}\left(R^2 + \frac{z^2}{q_i^2} \right) \right], \label{eq:deprojMGE}
\end{equation}
where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane. The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
\begin{eqnarray}
q_i^2 &=& \frac{q_i'^2 - \cos^2 i}{\sin^2 i}\\
\nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
\end{eqnarray}
%--------------------------------------------

@@

%--------------------------------------------
The free parameters of the lens model are: the source position $(x_s',y_s')$, the radial slope $\alpha$ and Fourier parameters $(a_k,b_k)$ of the lens mass distribution in Equations \eqref{eq:scalefreemodel}-\eqref{eq:Fourieransatz}. We want to minimize the distance between the observed image positions, $\vect{\theta}_{oi}$, and those predicted by the lensing model, $\vect{\theta}_{pi}$. To avoid having to solve the lens equation \eqref{eq:Fourierlenseq} for $\vect{\theta}_{pi}$, we follow \citet{1991ApJ...373..354K} and cast the calculation back to the source plane using the magnification tensor in Equation \eqref{eq:magnificationtensor} to approximate $\vect{\theta} \simeq (\partial \vect{\theta} / \partial \vect{\beta}) \vect{\beta} = \mathscr{M} \vect{\beta} $. The best fit lens model is then the one that minimizes
\begin{align}
\begin{split}
\chi^2_\text{lens} &= \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right) \left( \vect{\theta}_{pi} - \vect{\theta}_{oi} \right)\right|^2\label{eq:chi2lens}\\
&\simeq \sum_{i} \left|\left( \begin{matrix} \frac{1}{\Delta_x} & 0\\0 & \frac{1}{\Delta_y}\end{matrix}\right)  \left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}} \left( \begin{matrix} x_s' - \tilde{x}'_{si} \\ y_s' - \tilde{y}'_{si} \end{matrix} \right) \right|^2,
\end{split}
\end{align}
where $(\Delta_x,\Delta_y)$ are the measurement errors of the image positions $\vect{\theta}_{oi}$. $\left.\mathscr{M}\right|_{\vect{\theta}=\vect{\theta}_{oi}}$ is the magnification tensor and $(\tilde{x}'_{si},\tilde{y}'_{si})$ the source position according to the lens equation, both evaluated at the position of the $i$-th lensing image, $\vect{\theta}_{oi}$. Following \citet{GlennEC} we add a term
\begin{equation}
\chi^2_\text{shape} = \lambda \sum_{k \geq 3} \frac{\left(a_k^2 +b_k^2 \right)}{a_0^2} \label{eq:chi2shape}
\end{equation}
(with $\lambda$ being some weight factor) which forces the shape of the mass distribution to be close to an ellipse. The total $\chi^2$ to minimize is therefore
\begin{equation}
\chi^2 = \chi^2_\text{lens} + \chi^2_\text{shape} \label{eq:chi2total}
\end{equation}
We set $a_1 = b_1 = 0$, which corresponds to the choice of origin; in this case the center of the galaxy.

@@

%--------------------------------------------
As data we use stellar line-of-sight rotation velocities $v_\text{rot} = \langle v_\text{los} \rangle_\text{obs}$ and velocity dispersions $\sigma$ as described in Section \ref{sec:data_kinematics}. The JAM models give a prediction for the second line-of-sight velocity moment $\langle v_\text{los}^2 \rangle_\text{obs}$. The root-mean-square (rms) line-of-sight velocity $v_\text{rms}$ allows a data-model comparison by relating theses velocities according to 
\begin{equation}
 v_\text{rms}^2 = v_\text{rot}^2 + \sigma^2  \stackrel{!}{=} \langle v_\text{los}^2 \rangle_\text{obs}.
\end{equation}
\OLD{The model in Equation \eqref{eq:explicitLOSvelCap}}\NEW{The model derived from the Jeans equations as outlined in Section \ref{sec:model_JAM_JAM}} predicts the intrinsic $\langle v_\text{los}^2 \rangle_\text{intr}\equiv\langle v_\text{los}^2\rangle$ at a given position on the sky, which needs then to be modified to $\langle v_\text{los}^2 \rangle_\text{obs}$ according to the mode of observation to be comparable to the measurements. The measured $v_\text{rms}$ is a light-weighted mean for a pixel along the long-slit of the spectrograph, with width $L_y = 1''$ \citep{SWELLSV} and a certain given extent along the galaxy's major axis, $L_x$, i.e., for a rectangular aperture
\begin{equation}
\text{AP}(x',y') \equiv \left\{ \begin{array}{ll} 1 & \text{for } -\frac{L_x}{2} \leq x' < + \frac{L_x}{2}\\
& \text{and } - \frac{L_y}{2} \leq y' \leq + \frac{L_y}{2}  \\ 0 & \text{otherwise.} \end{array} \right.
\end{equation}
The light arriving at the spectrograph itself was subject to seeing, i.e., a Gaussian with Full Width Half Maximum (FWHM) of $1.1''$ \citep{SWELLSV},
\begin{equation}
\text{PSF}(x',y')\equiv\mathscr{N}(0,\sigma_\text{seeing}=\text{FWHM}/2\sqrt{2\ln2}).
\end{equation}
The model predictions for $\langle v_\text{los}^2 \rangle_\text{intr}$ have therefore to be convolved with the convolution kernel
\begin{eqnarray}
K(x',y') &\equiv& (\text{PSF} \ast \text{AP})(x',y') \nonumber\\
&=& \frac{1}{4} \prod_{u \in \{x',y'\}} \left[ \text{erf}\left( \frac{L_u/2 - u}{\sqrt{2}\sigma_\text{seeing}}\right) + \text{erf} \left( \frac{L_u/2 + u}{\sqrt{2} \sigma_\text{seeing}} \right) \right],
\end{eqnarray}
and weighted by the surface brightness $I(x',y')$, i.e.,
\begin{eqnarray}
I_\text{obs} &=& I \ast K\\
\langle v_\text{los}^2 \rangle_\text{obs} &=& \frac{(I \langle v_\text{los}^2\rangle_\text{intr}) \ast K}{I_\text{obs}}.
\end{eqnarray}
\NEW{We modified the JAM code by \citet{Cap08} to use this convolution kernel with non-square pixels. The JAM code then}\OLD{If provided with the convolution kernel, the JAM code\footnote{The IDL code package for Jeans Anisotropic Models (JAM) by \citet{Cap08} is available online at \url{http://www-astro.physics.ox.ac.uk/~mxc/software}. The version from June 2012 was used in this work.} by \citet{Cap08}} performs the convolution numerically. We set $L_x = 0.21''$ as the width of the model pixel, and get a prediction for the actual measurements in bins of width $0.63''$, $1.26''$ and $1.89''$ \citep{SWELLSV} as light-weighted mean from each 3, 6 and 9 model pixels.
%--------------------------------------------

@@

%--------------------------------------------
As mentioned above, JAM modelling allows to incorporate an invisible matter component in addition to the luminous matter in the form of an MGE. In Section \ref{sec:results_JAM_NFW} we will include a spherical Navarro-Frenk-White (NFW) DM halo \citep{1996ApJ...462..563N} in the dynamical model. The classical NFW profile has the form
\begin{equation}
\rho_\text{NFW}(r) \propto r^{-1} \left( r+r_s \right)^{-2} \label{eq:NFWprofile}
\end{equation}
and two free parameters, the scale length $r_s$ and a parameter describing the total mass of the halo. We will use $v_\text{200}\NEW{\equiv \sqrt{GM_{200}/r_{200}}}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological critical density $\rho_\text{crit} \equiv (2H^2)/(8\pi G)$, \OLD{i.e.,}\NEW{ and where $M_{200} \equiv M(<r_{200}) \stackrel{!}{=} \frac 43 \pi r_{200}^3 \cdot 200\rho_\text{crit}(z=0)$.}
\OLD{\begin{eqnarray*}
M_\text{200} &=& M(<r_{200})\\
\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
\end{eqnarray*}}
with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}. \OLD{How much the mass is concentrated in the center of the NFW halo is given by the concentration parameter
\begin{equation}
c_{200}\equiv r_{200} / r_s. \label{eq:NFW_c}
\end{equation}}
\NEW{The mass concentration of the NFW halo is quantified by $c_{200}\equiv r_{200} / r_s$.}
There is a close relation between the concentration and halo mass in simulations \citep{1996ApJ...462..563N}. \citet{Maccio08} found this relation for the WMAP5 cosmology to be
\begin{equation}
\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
\end{equation}
(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2). \NEW{In Section \ref{sec:results_JAM_NFW} we will use this relation as prior information to guide the modelling towards realistic NFW halo shapes.}
%--------------------------------------------

@@

The scaling of the drizzled HST/WFC3 images is  $S \equiv 0.05''/\text{pixel width}$ and the total exposure time $T = 1600$ sec. Each Gaussian in the MGE has a total F814W luminosity $L_i$ (in counts) and a central surface brightness (in counts per pixel) of
\begin{equation}
C_{0,i}\text{[counts/pixel]} = \frac{L_i[\text{counts}]}{2\pi \sigma_i[\text{pixel}]^2 q_i}.
\end{equation}
This is then transformed into an I-band surface brightness (in $\text{mag}\times(1'')^{-2}$) via
\begin{equation}
\mu_{I,0,i} \simeq -2.5 \log_{10}\left( \frac{C_{0,i}\text{[counts/pixel]}}{T[\text{sec}] \cdot S[''/\text{pixel width}]^2}\right) + Z + C + A_I, \label{eq:muI_}
\end{equation}
where $Z\simeq21.62~\text{mag}$ is the zero-point from \citet{Holtzman}, updated according to \citet{Dolphin,DolphinNew}, for the photometric system of the HST/WFPC2 camera and the F814W filter, plus a correction for the difference in gain between calibration and observation. $C= 0.1~\text{mag}$ corrects for the finite aperture of the WFPC2; and $A_I =0.015~\text{mag}$ is the extinction in the (Landolt) I-band towards J1331, according to the NASA/IPAC Extragalactic Database (NED)\footnote{The NASA/IPAC Extragalactic Database (NED, \url{https://ned.ipac.caltech.edu/}) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration. The data for J1331 (SDSS J133140.33+362811.9) was retrieved in October 2013.}. The colour-dependent correction between the F814W filter and the I-band of the UBVRI photometric system is  small \citep{Holtzman} and we neglect it therefore. The last step is to transform the surface brightness $\mu_{I,0,i}$ (in mag) to the I-band surface density $I_{0,i}$ (in $L_\odot$/pc$^2$) of the Gaussian, i.e.,
\begin{eqnarray}
I_{0,i}[L_\odot \text{pc}^{-2}] = \left( 64800/\pi\right)^2 \left(1+z_d \right)^4 10^{0.4\left(M_{\odot,I}-\mu_{I,0,i} \right)},
\end{eqnarray}
where the term with $z_d$ accounts for redshift dimming and $M_{\odot,I}=4.08~\text{mag}$ is the Sun's absolute I-band magnitude \citep{1998gaas.book.....B}. The luminosity $L_i$[counts] and the corresponding surface brightness density $I_{0,i} [L_\odot \text{pc}^{-2}]$ of each Gaussian are given in Table \ref{fig:MGEinnerRegions}.
%--------------------------------------------

@@

%--------------------------------------------
To estimate the inclination of J1331 with respect to the observer, we use the observed axis ratio of the flattest ellipse in the IRAF \emph{ellipse} model for J1331, which is $q'=0.42$. This is similar to the disk axis ratio of $q' = 0.40$ found by \citet{SWELLSI}. If a typical thickness of an oblate disk is around $q_0 \sim 0.2$ \citep{1958MeLu2.136....1H}, the inclination follows from 
\begin{equation}
\cos^2 i = \frac{q'^2 - q_0^2}{1 - q_0^2}
\end{equation}
and a correction of $+3^\circ$ \citep{1988ngc..book.....T}. Our estimate for the inclination is therefore $i \approx 70^\circ$. Given this inclination, the 2-dimensional MGE models can be deprojected into three dimensions (see Section \ref{sec:MGE_theo_deprojection}).

@@

For the velocity anisotropy parameter $\beta_z$ we will again employ a uniform prior 
\begin{equation}
p(\beta_z) = \mathscr{U}(-0.5,+0.5)
\end{equation}
to exclude very unrealistic anisotropies. The full prior used is then
\begin{align}
\begin{split}
&p(\Upsilon_\text{I,*},r_s,v_{200},\beta_z) \\
&= \frac{1}{\ln\left( 10 r_s\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta_z), 
\end{split}
\end{align}
where the factor $1/\ln\left( 10 r_s\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ to the fit parameters $(v_{200},r_s)$.
